Macro Impacts

### 2016-08-25 Macro Impacts Revised.tex
One other typo fixed

It gives results on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^-8$ results in $r_\te{fast melt} < r_X$ which is a bit of a problem.

>>>>

It gives results on the order of micrometers to tenths of micrometers for most marco radii which, for $r_X > 10^{-8}$ results in $r_\te{fast melt} < r_X$ which is a bit of a problem.
